Strings functions analysis

### 2022-08-22 article.tex
Unexpected advantage of immutability added
lang criteria added to used materials
"Why it’s not fixed yet by others?" added to introduction
introduction simplified

\documentclass[anonymous,sigplan,review,11pt,nonacm,natbib=false]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
\addbibresource{main.bib}

@@

\usepackage{debate}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

@@

    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria.

    An important factor for any function will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.

    Another important parameter that is investigated in this article is the number of uses of one function, inside (for realization) the others. This criterion allows us to identify important dependencies of some functions on others.

    An algorithm to obtain the minimum set of required string functions will be created. This algorithm will be analyzed for susceptibility to bias, since it depends on the initial input data.

    Also an important parameter for functions (in this case string functions) is their running time, so this article also considers this parameter. Since this is a complex analysis, the asymptotics of mutable and immutable string functions will be analyzed, as well as the asymptotics under full language immutability.

    The article then discusses the results obtained and evaluates them. The accuracy of the obtained data is also evaluated. And a conclusion is made: which set of functions we took for our language.

@@

@@

@@

>>>>

\documentclass[anonymous,sigplan,review,11pt,nonacm,natbib=false]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}

@@

\usepackage{rotating}
\usepackage{debate}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

    Most programming languages add functions to their string libraries without any limit on the number, for this reason there is no such research on this topic at the moment.

@@

    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing functions, but only those that meet some criteria. \hl{<- Transfer to method}

@@

% \begin{sideways} \end{sideways}

@@

    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.

@@

    https://yegor256.github.io/plum/
